Supplementary Material for _A Guide to Pre-processing High-Frequency Animal Tracking Data_

### 2021-09-29 supplement/05_calibration_data.Rmd
style code

>>>>

Compare number of receivers and SD and speed.

```{r, eval=FALSE, echo=FALSE}
data_nbs <- data[, c("NBS", "SD", "speed_in", "VARX", "VARY")]
data_nbs <- melt(
  data_nbs,
  id.vars = c("NBS")
)
```

```{r, eval=FALSE, echo=FALSE}
# plot heatmaps
fig_sd_nbs <-
  ggplot(data_nbs) +
  geom_jitter(
    aes(factor(NBS), SD, col = speed_in),
    size = 0.2,
    alpha = 0.4
  ) +
  geom_hline(
    yintercept = 100,
    lty = 2, col = "grey"
  ) +
  geom_vline(
    xintercept = 1.5,
    lty = 2, col = "grey"
  ) +
  scale_colour_viridis_c(
    option = "G", direction = -1,
    limits = c(0, 20),
    na.value = "red"
  ) +
  coord_cartesian(
    expand = F,
    xlim = c(0.5, 6),
    ylim = c(1, 1e3)
  ) +
  scale_y_log10() +
  theme_classic() +
  theme(
    # panel.border = element_rect(
    #   colour = "black",
    #   fill = "NA"
    # ),
    legend.key.width = unit(2, "mm"),
    legend.key.height = unit(5, "mm"),
    legend.position = c(0.8, 0.85),
    legend.background = element_blank()
  ) +
  # facet_wrap(~variable)+
  labs(
    colour = "Speed (m/s)",
    x = "# WATLAS receivers",
    y = "Positioning error (SD)"
  )

ggsave(
  fig_sd_nbs,
  filename = "supplement/figures/fig_sd_nbs.png",
  height = 5,
  width = 3
)
```

### 2021-09-29 supplement/06_bat_data.Rmd
style code

```{r localisation_error, echo=FALSE}
fig_error_histogram <-
  ggplot(data) +
  geom_histogram(
    aes(
      x = sqrt(VARX),
      fill = (sqrt(VARX) > 100)
    ),
    bins = 15,
    # fill = "grey",
    # col = "black",
    show.legend = F
  ) +
  scale_fill_viridis_d(
    option = "B",
    begin = 0.4,
    end = 0.8
  ) +
  scale_x_log10(
    breaks = c(1, 1000),
    labels = c("low", "high")
  ) +
  scale_y_sqrt() +
  coord_cartesian(
    xlim = c(0.5, 5e3)
  ) +
  theme_void()+
  theme(
    axis.text.y = element_blank(),
    axis.text.x = element_text(
      face = "bold",
      size = 16
    ),
    axis.title.y = element_blank(),
    axis.title.x = element_text(
      face = "bold",
      size = 16
    )
  ) +
  labs(x = "Positioning error")

@@

```{r echo=FALSE}
# plot bat data to examine for errors
fig_bat_raw <-
  ggplot(data) +
  geom_path(aes(X, Y,
    group = TAG,
    colour = TAG
  ),
  show.legend = FALSE
  ) +
  scale_colour_brewer(palette = "Dark2") +
  ggspatial::annotation_scale(location = "br") +
  theme_void()+
  theme(
    axis.text = element_blank(),
    axis.title = element_blank()
  ) +
  coord_sf(crs = 2039)
```

>>>>

```{r localisation_error, echo=FALSE}
fig_error_histogram <-
  ggplot(data) +
  geom_histogram(
    aes(
      x = sqrt(VARX),
      fill = (sqrt(VARX) > 100)
    ),
    bins = 15,
    # fill = "grey",
    # col = "black",
    show.legend = F
  ) +
  scale_fill_viridis_d(
    option = "B",
    begin = 0.4,
    end = 0.8
  ) +
  scale_x_log10(
    breaks = c(1, 1000),
    labels = c("low", "high")
  ) +
  scale_y_sqrt() +
  coord_cartesian(
    xlim = c(0.5, 5e3)
  ) +
  theme_void() +
  theme(
    axis.text.y = element_blank(),
    axis.text.x = element_text(
      face = "bold",
      size = 16
    ),
    axis.title.y = element_blank(),
    axis.title.x = element_text(
      face = "bold",
      size = 16
    )
  ) +
  labs(x = "Positioning error")

@@

```{r echo=FALSE}
# plot bat data to examine for errors
fig_bat_raw <-
  ggplot(data) +
  geom_path(aes(X, Y,
    group = TAG,
    colour = TAG
  ),
  show.legend = FALSE
  ) +
  scale_colour_brewer(palette = "Dark2") +
  ggspatial::annotation_scale(location = "br") +
  theme_void() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank()
  ) +
  coord_sf(crs = 2039)
```
